A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Electron Beam Dynamics

### 2019-01-31 paper/submission/theor-experiment.tex
new bib, small changes to paper

In addition to addressing the challenge of producing an optimized beam, 
this model was chosen to demonstrate the ability of the framework to tackle large problems.
Six design variables and objectives were used, along with three constraints.
The objectives include transverse and longitudinal beam sizes, 
transverse momentum, and longitudinal energy spread. 
The design variables include the two gun solenoids and 
the first four quadrupoles strengths. 
This problem encompasses high dimensionality 
and nonlinear effects such as space charge. There is no existing information
that accurately predicts optimized parameters for this beam line. 
This work is meaningful in that it will guide future operations at the AWA.

>>>>

In addition to addressing the challenge of producing an optimized beam, 
this model was chosen to demonstrate the ability of the framework to tackle large problems.
Six design variables and objectives were used, along with three constraints.
The objectives include transverse and longitudinal beam sizes, 
transverse momentum, and longitudinal energy spread. 
The design variables include the two gun solenoids and 
the first four quadrupoles strengths. 
This problem encompasses high dimensionality 
and nonlinear effects such as space charge. 
Using this model it was possible to find good solutions that meet the 
operational goals for the new beamline.  One of these solutions is 
presented in the next section.
